Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-26 proposal/prop.tex
prop

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{tensor}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

@@

By using the law of large numbers, quantum probabilities can be also
estimated by relative frequencies. For example, if we want to know the
probability of ``spin up'' in a Stern-Gerlach
experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}, we
can put a beam of silver atoms in a highly inhomogeneous magnetic
field, and count the number of atoms deflects up. Ideally, if the
local field of strength directs to the $z$-axis, and all particles
have the same velocity, the Stern-Gerlach experiment only produces two
spots corresponding to $\ket{0}$ and $\ket{1}$. Notice that whenever
the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal
measurement is picked, measuring the spin is exactly the same as
tossing a coin. In other words, if someone claims to be tossing a coin
behind a veil, and only shows the resulting heads or tails, we cannot
distinguish whether the results are really deriving from tossing a
coin, or by running a Stern-Gerlach experiment, and showing the head,
the tail, or the side of coin if the silver atoms is spin up, spin
down, or just hit the middle, respectively. Following our theme, a
Stern-Gerlach experiment requires significant resources to keep the
local field of strength directing to the $z$-axis precisely, to keep
the atoms having almost the same velocity, and to point out the exact
position each particle landed on. If the field of strength does not
perfectly direct to the $z$-axis, we do not really test the quantum
event we want to test. Even if the field of strength perfectly directs
to the $z$-axis, the variant velocity makes spots broader and more
washed out. Together with the precision limit of the detector, it may
sometimes be hard to decide a particle corresponding to which state.

>>>>

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=nyt,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
%% \usepackage[T1]{fontenc}
%% \usepackage[latin9]{inputenc}
\usepackage[utf8]{inputenc}
\usepackage{tensor}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

@@

Similarly to the classical case, it is possible to estimate quantum
probabilities by utilizing the frequentist approach of the previous
section, assuming identical measurements conditions in each repeated
experiment. For instance, if one wants to determine the probability
that the spin of a given silver atom is +$\hbar/2$, a Stern-Gerlach
apparatus is built where ideally an inhomogeneous magnetic field is
generated along, let's say, the quantization axis $z$. One then
produces a collimated beam of identically prepared (neutral) silver
atoms that is directed between the poles of the magnet where a
predetermined field-gradient along the $z$ direction has been
established. Under appropriate experimental conditions we will observe
that the beam, after traversing the magnetic-field region, will be
deflected towards two regions identified by distinguished spots on a
detector situated behind the
apparatus~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
Each of the two discrete values is associated to either +$\hbar/2$ or
-$\hbar/2$, commonly called ``spin up'' and ``spin down'',
respectively. By ``counting'' the number of atoms that are deflected
in the ``spin up'' region one can, in principle, estimate the
probability that the prepared state of the silver atom state has spin
+$\hbar/2$. Notice that a real experiment does not necessarily
represent an ``ideal measurement''. For example, not all silver atoms
will be identically prepared, or the field-gradient could not be large
enough to distinguish between the spin up and down situations simply
producing a large single blot. In other words, the closer we get to an
ideal measurement the better we determine those probabilities at the
cost of significantly increasing the number of resources. It is not
very well appreciated in the literature that Bohr attempted to argue
against the measurability of the spin of a free electron. Essentially,
Bohr argued (and Mott later on justified his assertion by an elegant
use of uncertainty relations~\cite{10.2307/j.ctt7ztxn5.15}) that a
Stern-Gerlach experiment could not succeed in establishing the spin of
an unbound electron because the Lorentz force would blur the detected
pattern. This example illustrates the case of a fundamental physical
limitation that not even infinite resources could mitigate.
